Enhancement of SDR in Thessaloniki

### 2024-04-12 high_aod/GHI_enh_02_ID_CE.tex
Commit 2024-04-12 11:11

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-04-10}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{verbatim}
[1] "/home/athan/MANUSCRIPTS/02_enhancement/high_aod"
\end{verbatim}

\begin{verbatim}
Warning:

 ** Test is active!! ** 
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\ControlFlowTok{switch}\NormalTok{(csmodel,}
       \AttributeTok{Exact\_B.Exact\_W =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.02}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}} \DecValTok{55}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_2\_B.Low\_2\_W =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.03}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{5}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_B.Exact\_W   =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.04}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}} \DecValTok{20}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_B.High\_W    =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.05}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}} \DecValTok{20}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_B.Low\_W     =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.05}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.18}\NormalTok{\},}
       \AttributeTok{High\_B.Low\_W    =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.10}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.25}\NormalTok{\}, }\DocumentationTok{\#\# same as the used criterio}
\NormalTok{                         \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \DecValTok{1}\NormalTok{   ; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \DecValTok{1}\NormalTok{   \})}
\DocumentationTok{\#\# init flag}
\NormalTok{DATA[, Enhanc\_C\_4 }\SpecialCharTok{:=} \ConstantTok{FALSE}\NormalTok{]}

@@

\begin{verbatim}
 [1]        NA        NA 1.0440020 0.9584892 0.8852695 0.8218832 0.7664852 0.7176648 0.6743248
[10] 0.6355989 0.6007941
\end{verbatim}

@@

\begin{longtable}[]{@{}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}@{}}
\caption{Enhanc\_C\_4}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedleft
FALSE
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
TRUE
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedleft
FALSE
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
TRUE
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
6031301 & 170866 \\
\end{longtable}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-191} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-192} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-193} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-194} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-195} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-196} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-197} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-198} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-199} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-200} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-201} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-202} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-203} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-204} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-205} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-206} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-207} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-208} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-209} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-210} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-211} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-212} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-213} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-214} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-215} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-216} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-217} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-218} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-219} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-220} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-221} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-222} \end{center}

@@

\begin{verbatim}
Warning: TEST IS ACTIVE !!
\end{verbatim}

TEST IS ACTIVE !!

@@

\begin{verbatim}
2024-04-10 14:41:06.4 athan@tyler GHI_enh_02_ID_CE.R 8.094902 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-04-12}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{Shaded}
\begin{Highlighting}[]
\DocumentationTok{\#\# \_\_ Document options {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\ControlFlowTok{switch}\NormalTok{(csmodel,}
       \AttributeTok{Exact\_B.Exact\_W =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.02}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}} \DecValTok{55}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_2\_B.Low\_2\_W =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.03}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{5}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_B.Exact\_W   =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.04}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}} \DecValTok{20}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_B.High\_W    =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.05}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}} \DecValTok{20}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_B.Low\_W     =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.05}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.18}\NormalTok{\},}
       \AttributeTok{High\_B.Low\_W    =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.11}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.31}\NormalTok{\}, }\DocumentationTok{\#\# same as the used criterio}
\NormalTok{                         \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \DecValTok{1}\NormalTok{   ; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \DecValTok{1}\NormalTok{   \})}
\DocumentationTok{\#\# init flag}
\NormalTok{DATA[, Enhanc\_C\_4 }\SpecialCharTok{:=} \ConstantTok{FALSE}\NormalTok{]}

@@

\begin{verbatim}
 [1]        NA        NA 1.0941141 1.0026612 0.9243490 0.8565476 0.7972846
 [8] 0.7450515 0.6986754 0.6572300 0.6199744
\end{verbatim}

@@

\begin{longtable}[]{@{}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}@{}}
\caption{Enhanc\_C\_4}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedleft
FALSE
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
TRUE
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedleft
FALSE
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
TRUE
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
6072539 & 129628 \\
\end{longtable}

@@

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-4} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-5} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-6} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-7} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-8} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-9} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-10} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-11} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-12} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-13} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-14} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-15} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-16} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-17} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-18} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-19} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-20} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-21} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-22} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-23} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-24} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-25} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-26} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-27} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-28} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-29} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-30} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-31} \end{center}

@@

\begin{verbatim}
2024-04-12 07:30:18.5 athan@sagan GHI_enh_02_ID_CE_highAOD.R 31.981997 mins
\end{verbatim}
